% ═══════════════════════════════════════════════════════════════
%  Acknowledgements
% ═══════════════════════════════════════════════════════════════
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

The completion of this end-of-studies internship report would not have been possible without the guidance, support, and collaboration of numerous individuals to whom I owe a sincere debt of gratitude.

I would first like to express my deepest appreciation to my academic supervisor, \textbf{Mr.\ KERZAZI}, for his invaluable guidance, constructive feedback, and continued encouragement throughout the duration of this internship. His technical insight and pedagogical rigor have been instrumental in shaping the direction of this work.

I extend my warmest thanks to the entire team at \textbf{IBM Client Innovation Center (CIC) Morocco} and \textbf{Hakkoda} for welcoming me into their organization and for the exceptional professional environment they provided. Working alongside experienced Data Engineers and DevOps practitioners has been a genuinely enriching and formative experience.

Special thanks are owed to my industrial supervisor and colleagues at the Hakkoda team for their patience, technical mentorship, and willingness to share their expertise on Snowflake platform engineering, CI/CD automation, and cloud data architecture. Their day-to-day guidance was indispensable to the progress of this project.

I am equally grateful to the faculty of the \textbf{École Nationale Supérieure d'Informatique et d'Analyse des Systèmes (ENSIAS)}, whose rigorous academic program provided the theoretical and technical foundation upon which this internship was built.

Finally, I wish to express my profound gratitude to my family and friends for their unconditional support, patience, and encouragement throughout my studies. Their belief in my abilities has been a continuous source of motivation.

\vspace{1cm}
\begin{flushright}
  Mouad MOULAY RACHID\\
  Rabat, 2025
\end{flushright}
\newpage
